### 2021-03-05 paper_1.tex
update paper_1

\subsection{Introduction}
In order to reduce the complexity in the analysis of a scene, a useful method is introduced to be able to detect potential information, such as regions or objects, simultaneously. This method is called "Visual saliency". Before introducing the topic, four types of concepts must be explained: (1) Fixations: they concern the scene framed by the human eye and are used to compare the methods of forecasting fixations. (2) ROI: each region contains information where there is difficulty in separating objects, such as clear ones. (3) Salient objects: animals, people, cars etc. (4) Outline of salient objects. The proposed method is based on carrying out a Salient Structure (SS) Detection, useful for identifying the four previous properties, both in disordered and simple scenes. The proposed framework is called CGVS (contour-guided visual search): this visual search tool identifies the targets using two types of paths: (1) selective path: the contours of each object are detected, useful for estimating the position and size of the ROI: (2) non-selective path: it can be properties such as color, luminary, texture etc.
This search strategy carries out parallel processing on both paths, extracting global and local information. Finally, a Bayesian inference is applied to integrate the contour based spatial prior (CBSP), a useful method for extracting information on the contours, and local information in order to identify the salience of each pixel.

>>>>

\subsection{Introduction}
In order to reduce the complexity in the analysis of a scene, a useful method 
is introduced to detect potential information, such as regions or 
objects, simultaneously. This method is called "\emph{Visual Saliency}". Before introducing
the topic, four types of concepts must be explained: (1)\emph{Fixations}: 
they concern the scene framed by the human eye. They are used to compare 
the methods of forecasting fixations. (2)\emph{ROI}: each region contains information, 
such as light or dark objects, which is intended to be separated.(3)\emph{Salient objects}: 
animals, people, cars etc. (4)\emph{Salient edges}: boundary of each object. The proposed 
method is based on carrying out a \emph{Salient Structure (SS) Detection},
useful for identifying the four previous properties, both in cluttered and 
simple scenes. The proposed framework is called \emph{CGVS (contour-guided visual 
search)}. This visual search tool identifies the targets using two types of 
paths: (1)\emph{selective path}: the boundaries of each object are detected, useful 
for estimating the position and size of the ROI: (2)\emph{non-selective path}: it 
can be properties such as color, luminary, texture etc. This search strategy 
carries out parallel processing on both paths, extracting global and local 
information. Finally, a Bayesian inference is applied to integrate the contour 
based spatial prior (CBSP), a useful method for extracting information on 
the boundaries, and local information in order to identify the salience of each 
pixel.
